\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-16 manuscript/manuscript.tex
updated

\subsection{Likelihood Demand Trend Projection}
The likelihood demand trend projection policy we will investigate is an adaptive likelihood method that uses multiple runs of 15-week data to assume the same trends hold for future data. 
The given data suggests that each price reduction has a compounding effect on the unit volume sold. 
For instance, 10\% off increases unit sales by 30\%, and 20\% increases unit sales by 75\% compared to previous periods. 
The model uses rules based on the sales increase per price category to estimate the unit sales for the remaining periods. 
To accomplish this the price distribution for the current model is added to the observed price distributions and the model evaluates the estimated likelihood of “out of stock condition”. 
In other words, if the estimated units sold by the end of the 15 weeks is less than the remaining units, the model increases the discount to stimulate the forecasted demand.

>>>>

\subsection{Likelihood Demand Trend Projection}
The likelihood demand trend projection policy is an adaptive likelihood method that uses multiple runs of 15-week data to assume the same trends hold for future data. 
The given data suggests that each price reduction has a compounding effect on the unit volume sold. 
For instance, 10\% off increases unit sales by 30\%, and 20\% increases unit sales by 75\% compared to previous periods. 
The model uses rules based on the sales increase per price category to estimate the unit sales for the remaining periods. 
To accomplish this the price distribution for the current model is added to the observed price distributions and the model evaluates the estimated likelihood of “out of stock condition”. 
In other words, if the estimated units sold by the end of the 15 weeks is less than the remaining units, the model increases the discount to stimulate the forecasted demand.
